### 2014-11-13 evaluation.tex

Figure~\ref{grf:BA} shows the performance of operations in bank account example
as we increase the number of clients in \cf{1DC} configuration.. Our client
workload was generated using YCSB benchmark~\cite{YCSB}. The benchmark
uniformly chose from 100,000 keys, where the operation spread was 25\%
withdraw, 25\% deposit and 50\% getBalance, which corresponds to the default
50:50 read:write mix in YCSB. We increased the number of clients from 128 to
1024, and each experiment ran for 180 seconds.

@@

Finally, we study the impact of summarization in
Figure~\ref{grf:summarization}. We use 128 clients and a single \name replica,
with all clients operating on the \emph{same} LWW register to stress test the
summarization mechanism. The shim layer cache (memory) is summarized every 64
updates, while the updates in the backing store (disk) are summarized every
4096 updates. Each point in the graph represents the average latency of the
previous 1000 operations. Each experiment is run for one minute.  Without
summarization, the average latency of operations increases exponentially to
almost one second, and only 13K operations were performed in a minute. Since
every operation has to reduce over the set of all previous operations,
operations take increasingly more time to complete since they must contend with
an ever growing set.  With summarization only in memory, performance still
degrades due to the cost of fetching all previous updates from the backing
store into the shim layer. Fetching the latest updates is essential for SC
operations. With summarization enabled on both disk and memory, latency does
not increase over time, and the implementation realizes throughput of 67K
operations/minute.

>>>>

Figure~\ref{grf:BA} shows throughput vs. latency of operations in the bank
account example as we increase the number of clients in a \cf{1DC}
configuration. Our client workload was generated using the YCSB
benchmark~\cite{YCSB}. The benchmark uniformly chooses from 100,000 keys, where
the operation spread was 25\% withdraw, 25\% deposit and 50\% getBalance, which
corresponds to the default 50:50 read:write mix in YCSB. We increased the
number of clients from 128 to 1024, and each experiment ran for 180 seconds.

@@

Finally, we study the impact of summarization in
Figure~\ref{grf:summarization}. We use 128 clients and a single \name replica,
with all clients operating on the \emph{same} LWW register to stress test the
summarization mechanism. The shim layer cache (memory) is summarized every 64
updates, while the updates in the backing store (disk) are summarized every
4096 updates. Each point in the graph represents the average latency of the
previous 1000 operations. Each experiment is run for one minute.  Without
summarization, the average latency of operations increases exponentially to
almost one second, and only 13K operations were performed in a minute. Since
every operation has to reduce over the set of all previous operations,
operations take increasingly more time to complete since they must contend with
an ever growing set.  With summarization only in memory, performance still
degrades due to the cost of fetching all previous updates from the backing
store into the shim layer. Fetching the latest updates from the backing store
is essential for SC operations. With summarization enabled on both disk and
memory, latency does not increase over time, and the implementation realizes
throughput of 67K operations/minute.
